Physcraper: Body

### 2020-07-10 2-body.Rmd
typo

We envision Physraper as an staple tool to make data connections across databases in a phylogenetic context for the advantage of phylogenetics and biology in general, as well as an effort towards fully reproducible workflows in phylogenetics.

>>>>

We envision Physraper as a staple tool to make data connections across databases in a phylogenetic context for the advantage of phylogenetics and biology in general, as well as an effort towards fully reproducible workflows in phylogenetics.
